Singapore's Public Housing Affordability

### 2023-11-06 datastory.qmd
Weekly Update

```{r, eval=TRUE,echo=FALSE}
library(shiny)
library(ggplot2)

# Placeholder example using the pressure dataset
ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_line() +
  labs(title = "Title", x = "x-axis", y = "y-axis")
```

>>>>

```{r, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
# Load the required libraries
library(tidyverse)
library(tidyr)
library(ggplot2)
library(scales)
```

```{r, eval=TRUE,echo=FALSE}
# Load the datasets
data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")

average_prices_1999 <- data1999 %>%
  group_by(flat_type) %>%
  summarise(AveragePrice1999 = mean(resale_price))

average_prices_2022 <- data2022 %>%
  group_by(flat_type) %>%
  summarise(AveragePrice2022 = mean(resale_price))

combined_data <- merge(average_prices_1999, average_prices_2022, by = "flat_type")

long_data <- pivot_longer(combined_data, cols = -flat_type, names_to = "Year", values_to = "AveragePrice")

ggplot(long_data, aes(x = flat_type, y = AveragePrice, group = Year, color = Year)) +
  geom_line() +
  geom_point() +
  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = 1, check_overlap = TRUE) +
  scale_y_continuous(labels = label_comma()) + 
  labs(title = "Average Resale Price Increment for Each Flat Type (1999 vs 2022)",
       x = "Flat Type",
       y = "Average Resale Price",
       color = "Year") +
  theme_minimal()
